
\begin{thebibliography}{19}


%\bibitem{}E. Sklar, S. Parsons, and P. Stone. Using RoboCup in university-level computer science education. Journal on Educational Resources in Computing (JERIC), Special Issue on robotics in undergraduate education, part I, 4(2), September 2004

\bibitem{pyro} D.S. Blank, D. Kumar, L. Meeden, and H. Yanco. Pyro: A python-based versatile programming environment for teaching robotics. Journal on Educational Resources in Computing(JERIC), Special issue on robotics in undergraduate education. Part 2, 4(3):115, 2004.

\bibitem{nqc} Baum. NQC. http://bricxcc.sourceforge.net/nqc/, accessed March 17, 2011.

\bibitem{brickos} Markus. brickOS. http://brickos.sourceforge.net/, accessed March 17, 2011.

\bibitem{lejos} J. Solorzano. leJOS. http://lejos.sourceforge.net/, accessed March 17, 2011.

\bibitem{mrds} Microsoft Robotics Developer Studio, http://www.microsoft.com/robotics/, accessed March 17, 2011.

\bibitem{startlogo} MIT's Scheller Teacher Education Program (STEP), http://education.mit.edu/ drupal/starlogo-tng, accessed March 17, 2011.

\bibitem{etoys} http://www.squeakland.org/, accessed March 17, 2011.

\bibitem{scratch} http://scratch.mit.edu/, accessed March 17, 2011.

\bibitem{robolab} Tufts University. RoboLab. http://www.ceeo.tufts.edu/robolabatceeo/, accessed March 17, 2011.

\bibitem{robolab-ext} M. Q. Azhar, An agent-oriented behavior-based interface framework for educationa robotics, In Agent-Based Systems for Human Learning (ABSHL) Workshop at Autonomous Agents and MultiAgent Systems (AAMAS-2006),2006.

\bibitem{braitenberg} V. Braitenberg, Vehicles: Experiments in Synthetic Psychology, MIT Press, Cambridge, 1986.

\bibitem{subsumicion} R. C. Arkin, Behavior-Based Robotics, MIT Press, Cambridge, 1998.

\bibitem{topologicalSorting}  H. Cormen, C. E. Leiserson, R. L. Rivest, C. Stein, Topological Sort, Introduction to Algorithms, MIT Press, Cambridge, 2009.

\bibitem{khepera} K-Team, Khepera I, http://www.k-team.com/, accessed March 17, 2011. 

\bibitem{exabot} Sol Pedre, Pablo de Cristóforis, Javier Caccavelli and Andrés Stoliar, A mobile mini robot architecture for research, education and popularization of science, Journal of Applied Computer Science Methods, Guest Editors: Jacek Zurada and Pablo Estevez, vol 2, no 1 pp 41-59, ISSN 1689-9636. 

\bibitem{yaks} Yet Another Khepera Simulator, http://freshmeat.net/projects/yaks/, accessed March 17, 2011. 

\bibitem{player} Player/Stage Simulator, http://playerstage.sourceforge.net/, accessed March 17, 2011.
%\bibitem{talleres} Science workshops, http://www.fcen.uba.ar/dov/talleres_de_ciencia/TALLERES_de_ciencia.htm, accessed March 17, 2011. 
\bibitem{expouba} ExpoUBA 2010, Plaza de las Ciencias, Universidad de Buenos Aires, Argentina, http://www.uba.ar/expouba, accessed March 17, 2010. %http://exactas.uba.ar/institucional/display.php?estructura=1\&desarrollo=0\&id\_caja=238\&nivel\_caja=2

\bibitem{taller2006} Robot programming workshop for high school students, www.fcen.uba.ar /dov/talleres\_de\_ciencia/2006/computacion.htm, accessed March 17, 2011. 

\bibitem{taller2009} Robot programming workshop for high school students, www.fcen.uba.ar /dov/talleres\_de\_ciencia/2009/computacion.htm, accessed March 17, 2011.

\end{thebibliography}